Fractional Types

### 2016-12-19 typespp.tex
Add some text for dual

@@

Given a \textrm{/-combinator} $p : \#c \leftrightblackspoon \#d$ which is a
morphism in the compact closed category, we can build circuits that construct
the \texttt{name} $\ulcorner{p}\urcorner$ and \texttt{coname}
$\llcorner{p}\lrcorner$ of $p$. These are shown in figure~\ref{fig:name-coname}.

\begin{figure}[ht]
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
      \path (-1.1,1) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (0,1);

@@

\begin{figure}
  \centering
  \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
    \path (-1,1) edge node[above] {\footnotesize{$1/{\textsf{\#d}}$}} (0,1);

    \path (1,1.75) edge node[above] {\footnotesize{${\#id}$}} (2,1.75);
    \path (1,0.25) edge node[above] {\footnotesize{${1/\textsf{\#d}}$}} (4,0.25);

    \path (3,2.25) edge node[above] {\footnotesize{$1/\textsf{\#c}$}} (8,2.25);
    \path (3,1.25) edge node[above] {\footnotesize{$\textsf{\#c}$}} (4,1.25);

    \draw (4,-0.25) -- (5,-0.25) -- (5,1.75) -- (4,1.75) -- cycle;
    \node at (4.5,0.75) {\footnotesize{$\texttt{cong}^{l}$}};
    \path (4.5,-0.25) edge node[right] {\footnotesize{$p : \#c \leftrightblackspoon \#d$}} (4.5,-0.75);

    \path (5,0.25) edge node[above] {\footnotesize{$1/\textsf{\#d}$}} (6,0.25);
    \path (5,1.25) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (6,1.25);

    \path (7,0.75) edge node[above] {\footnotesize{${\#id}$}} (8,0.75);

    \path (9,1.5) edge node[above] {\footnotesize{$1/{\textsf{\#c}}$}} (10,1.5);
  \end{tikzpicture}
  \caption{\label{fig:dual} Dual}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

>>>>

\subsection{\texttt{dual}}

Given a \textrm{/-combinator} $p : \#c \leftrightblackspoon \#d$ which is a
morphism in the compact closed category, we have a dual morphism
$p^{\ast} : 1/\#d \leftrightblackspoon 1/\#c$. This is shown by building a
reversible circuit in figure~\ref{fig:dual}.

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
    \path (-1,1) edge node[above] {\footnotesize{$1/{\textsf{\#d}}$}} (0,1);

    \path (1,1.75) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (2,1.75);
    \path (1,0.25) edge node[above] {\footnotesize{${1/\textsf{\#d}}$}} (4,0.25);

    \draw[dashed] (3.2,1.25) -- (3.2,2.25);
    \path [highlight] (3,2.25) edge node[above] {} (8,2.25);
    \path (3,2.25) edge node[above] {\footnotesize{$1/\textsf{\#c}$}} (8,2.25);
    \path [highlight] (3,1.25) edge node[above] {} (4,1.25);
    \path (3,1.25) edge node[above] {\footnotesize{$\textsf{\#c}$}} (4,1.25);

    \draw (4,-0.25) -- (5,-0.25) -- (5,1.75) -- (4,1.75) -- cycle;
    \node at (4.5,0.75) {\footnotesize{$\texttt{cong}^{l}$}};
    \path (4.5,-0.25) edge node[left] {\footnotesize{$p : \#c \leftrightblackspoon \#d$}} (4.5,-0.75);

    \draw[dashed] (5.8,0.25) -- (5.8,1.25);
    \path [highlight] (5,0.25) edge node[above] {} (6,0.25);
    \path (5,0.25) edge node[above] {\footnotesize{$1/\textsf{\#d}$}} (6,0.25);
    \path [highlight] (5,1.25) edge node[above] {} (6,1.25);
    \path (5,1.25) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (6,1.25);

    \path (7,0.75) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (8,0.75);

    \path (9,1.5) edge node[above] {\footnotesize{$1/{\textsf{\#c}}$}} (10,1.5);
  \end{tikzpicture}
  \caption{\label{fig:dual} Dual}
\end{figure}

@@

We also show circuits that construct the \texttt{name} $\ulcorner{p}\urcorner$
and \texttt{coname} $\llcorner{p}\lrcorner$ of $p$, in
figure~\ref{fig:name-coname}.

\begin{figure}[htb]
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
      \path (-1.1,1) edge node[above] {\footnotesize{${\textsf{\#id}}$}} (0,1);

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
